\documentclass[11pt,a4paper]{article}

% Fonts: TeX Gyre Pagella with matching math (Palatino-style, conventional academic look)
% Loaded by file name because the TeX Live OpenType files are not registered
% with the OS font database on most Linux distributions.
\usepackage{fontspec}
\usepackage{unicode-math}
\setmainfont{texgyrepagella}[
  Extension      = .otf,
  UprightFont    = *-regular,
  BoldFont       = *-bold,
  ItalicFont     = *-italic,
  BoldItalicFont = *-bolditalic,
]
\setmathfont{texgyrepagella-math.otf}
\frenchspacing

% Page layout
\usepackage[margin=1in]{geometry}

% Math
\usepackage{amsmath,amsthm}

% Tables
\usepackage{booktabs}

% Float placement (provides [H] specifier for strict inline placement)
\usepackage{float}

% Captions: small, bold-labelled
\usepackage{caption}
\captionsetup{font=small,labelfont=bf}

% Enumerated lists
\usepackage{enumitem}

% Prevent orphaned headings
\usepackage{needspace}

% Paragraph formatting
\usepackage{parskip}
\emergencystretch=1em
\hyphenpenalty=200

% Typographic refinement (better letter spacing, hyphenation, line breaks)
\usepackage{microtype}

% Tighter bibliography spacing
\usepackage{etoolbox}
\AtBeginEnvironment{thebibliography}{\setlength{\itemsep}{4pt plus 0.5pt}\setlength{\parsep}{0pt}}

% Colour expressions for hyperref
\usepackage{xcolor}

% Hyperlinks (subtle dark-blue, all-clickable)
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  allcolors=blue!50!black,
  pdfauthor={K.R. Ryan},
  pdftitle={The Geometric Siphon II: Directional Properties}
}

% Running header on pages 2+
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\itshape K.R.\ Ryan}
\fancyhead[R]{\small\itshape The Geometric Siphon II}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
% Title page (page 1) suppresses the running header
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[C]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
}

% Theorem environments
\newtheorem{theorem}{Theorem}
\setcounter{theorem}{3} % Start at Theorem 4

\theoremstyle{definition}
\newtheorem*{notation}{Notation}

\title{The Geometric Siphon II: Directional Properties}

% No paragraph indent, space between paragraphs (match Paper I)
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\begin{document}
\thispagestyle{plain}

\begin{center}
{\LARGE\bfseries The Geometric Siphon II: Directional Properties}

\vspace{12pt}
{\large K.R.\ Ryan}\\[4pt]
{\small Independent Researcher}\\[2pt]
{\small \href{mailto:gancor@gancor.xyz}{gancor@gancor.xyz} \quad|\quad ORCID: 0009-0004-6295-7040}

\vspace{8pt}
March 2026

\vspace{6pt}
{\small\textbf{Keywords:} concentrated liquidity, geometric residual, directional asymmetry,\\
exit asymmetry, Uniswap V3, Aerodrome, DeFi mechanism design}
\end{center}

\vspace{8pt}
\hrule
\vspace{12pt}

\begin{abstract}
In a companion paper (Ryan, 2026a), I identified the Geometric Siphon, a mechanism by which concentrated-liquidity (CL) positions sharing a depositor-level token balance transfer capital between positions under autonomous rebalancing. A token-ratio mismatch between the old and new tick ranges produces residuals that flow through the shared balance. This paper establishes three results on the directional properties of the residual.

For a rebalance into a new range of equal width recentred on the current price, Theorem~4 shows that the absolute residual $|\Delta R|$ increases strictly with displacement from the midpoint of the original range, up to the range boundary. Theorems~5 and~6 concern pools pairing a volatile asset at $T_0$ with a stablecoin at $T_1$ in Uniswap V3's pair ordering. Under symmetric sqrt-price displacements $\pm\delta$ that leave both displaced prices in range, the up-move position retains strictly more USD-denominated value than the down-move (Theorem~5). Under symmetric displacement past the range boundary, a below-range exit retains strictly less USD value than an above-range exit (Theorem~6) for the same pair ordering. Because residual magnitudes scale with position value, USD-denominated residuals inherit the same asymmetry.

All three results are verified by Foundry tests against a harness implementing exact Uniswap V3 \texttt{TickMath} and amount-equation constants. Across 36{,}337 rebalance events on 58 positions over 18 days on Aerodrome (Base), observed dust flows match the predicted direction: rising markets produce USD-denominated flow about $5\times$ larger than falling markets, despite a near-identical frequency of positive-dust events.
\end{abstract}

\section{Introduction}

Ryan (2026a) established that a CL rebalance produces a zero geometric residual if and only if the old and new ranges demand the same token ratio at current price (Theorem~1), that single-pool positions sharing a contract balance converge to equal value under repeated rebalancing (Theorem~2), and that positions rebalancing without swaps decay geometrically (Theorem~3). Those results characterise the existence, equilibrium and extinction behaviour of the siphon. They do not address how the residual responds to displacement magnitude, price direction or exit type.

This paper fills that gap with three theorems characterising the directional properties of the residual. Theorem~4 (Residual Monotonicity) establishes strict monotonicity of $|\Delta R|$ in displacement up to the range boundary. Theorem~5 (Directional Asymmetry) establishes an asymmetry in USD-denominated position value under symmetric sqrt-price displacement, for volatile/stablecoin pairs with the volatile asset at $T_0$. Theorem~6 (Exit Asymmetry) establishes an asymmetry in USD-denominated position value between above-range and below-range exits at symmetric displacement past the boundary, for the same pair ordering. Because residual magnitudes scale with position value, USD-denominated residuals inherit the asymmetries of Theorems~5 and~6.

\subsection{Scope}

This paper analyses Phase~3 operational data from a live CL portfolio management system on Aerodrome (Base).

\begin{table}[H]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Period & 6–24 March 2026 (18 days) \\
Positions & 58 across 5 depositor groups \\
Events & 36,337 rebalance events \\
Contract versions & PM V8, PM V9 \\
DEX & Aerodrome Slipstream (Base) \\
\bottomrule
\end{tabular}
\end{table}

\noindent The larger dataset enables detection of effects not observable at Phase~2 scale.

\subsection{Preliminaries from Ryan (2026a)}

For a position with liquidity $L$ in tick range $[s_a, s_b]$ at current sqrt price $s$, the Uniswap V3 amount equations give
\begin{equation}\label{eq:amounts-prelim}
x = L \cdot \left(\frac{1}{s} - \frac{1}{s_b}\right), \quad y = L \cdot (s - s_a)
\end{equation}
where $x$ is token0 (lower address) and $y$ is token1 (higher address). The position value in token1 units is
\begin{equation}\label{eq:value-prelim}
V = L \cdot \phi(s, s_a, s_b), \qquad \phi(s, s_a, s_b) = 2s - s^2/s_b - s_a.
\end{equation}

Theorem~1 (Ryan, 2026a) establishes that a rebalance from range $[s_a, s_b]$ to $[s_{a'}, s_{b'}]$ at current sqrt price $s$ produces a zero geometric residual if and only if the old and new ranges demand the same token ratio at $s$. Range equality is a sufficient condition but not the only one; any range change that shifts the required token ratio produces a non-zero residual, with the sign determined by which token is the binding constraint in the new range's mint.

The results below characterise how the magnitude and USD valuation of that residual respond to displacement direction, displacement magnitude and exit type.

\subsection{Notation}

Following Ryan (2026a):

\begin{itemize}[nosep]
    \item $s = \sqrt{p}$, the current sqrt price
    \item $[s_a, s_b]$, position range boundaries in sqrt-price space
    \item $L$, position liquidity
    \item $w = s_b - s_a$, range width in sqrt-price space
    \item $\delta$, displacement from range centre in sqrt-price space
    \item $nd = \delta / (w/2)$, normalised displacement ($0$ = centre, $1$ = range edge)
    \item $D$, dust flow (USD-denominated net position value change from non-swap sources)
    \item $\Delta R$, geometric residual (token surplus from a token-ratio mismatch between old and new ranges at current price)
\end{itemize}

Uniswap V3 places token0 at the pool's lower contract address. Theorems~5 and~6 below are stated for pools in which the volatile asset occupies $T_0$ (and the stablecoin $T_1$); in pools with the opposite address ordering, the USD-denominated inequalities invert but the mechanism is unchanged.

\section{Theoretical results}

\subsection{Theorem 4 (Residual Monotonicity)}

\begin{theorem}[Residual Monotonicity]
For a CL position in range $[s_a, s_b]$ rebalanced to a new range of equal width centred on the current sqrt price $s$, where $s$ has been displaced by $\delta$ from the midpoint $\bar{s} = (s_a + s_b)/2$, the absolute geometric residual $|\Delta R|$ increases strictly monotonically with $|\delta|$ for $|\delta| \leq w/2$.
\end{theorem}

\begin{proof}
Consider a position with liquidity $L$ in range $[s_a, s_b]$ at current sqrt price $s = \bar{s} + \delta$, where $\bar{s} = (s_a + s_b)/2$ is the range midpoint and $w = s_b - s_a$. The withdrawn token amounts are
\begin{equation}
x_w = L \cdot \left(\frac{1}{s} - \frac{1}{s_b}\right), \quad y_w = L \cdot (s - s_a)
\end{equation}

The new range, centred on $s$ with the same width $w$, has boundaries $s_{a'} = s - w/2$ and $s_{b'} = s + w/2$. At the range midpoint ($\delta = 0$), $R_{\text{old}} = R_{\text{new}}$ and the residual is zero by Theorem~1 (Ryan, 2026a).

For upward displacement ($\delta > 0$), $x_w$ is strictly decreasing in $\delta$ (since $\partial x_w / \partial s = -L/s^2 < 0$) whilst $y_w$ is strictly increasing ($\partial y_w / \partial s = L > 0$). As $s$ moves above the midpoint, the position becomes increasingly token1-heavy. The new range, centred on $s$, demands a ratio closer to 50/50 at its midpoint, requiring more token0 than the old position holds. Token0 is therefore the binding constraint.

The new liquidity is set by the token0 constraint:
\begin{equation}
L_{\text{new}} = \frac{x_w}{1/s - 1/s_{b'}} = \frac{L(1/s - 1/s_b)}{1/s - 1/(s + w/2)}
\end{equation}

The token1 surplus (residual) is $y_w - L_{\text{new}}(s - s_{a'})$. As $\delta$ increases, $x_w$ decreases (the binding constraint tightens) whilst $y_w$ increases (more surplus token1 is available). The fraction of total withdrawn value that can be deposited into the new range therefore decreases monotonically with $\delta$, and the absolute surplus increases monotonically.

At $\delta = w/2$, the position has fully exited range ($s = s_b$), $x_w = 0$, $y_w = L \cdot w$, and the position is 100\% token1. The residual equals the full token1 balance minus what can be deposited, which is the maximum possible residual.

The downward displacement case ($\delta < 0$) is symmetric: $y_w$ decreases, $x_w$ increases, and token0 enters surplus.
\end{proof}

\noindent\textit{Foundry verification.} Five in-domain displacement levels on a $1{,}000$-tick-wide position at price ${\sim}\$2{,}500$ (so $|\delta| \leq w/2 = 500$ ticks).

\begin{table}[H]
\centering
\begin{tabular}{@{}lrl@{}}
\toprule
Displacement (ticks) & Dust (USD) & Monotonic \\
\midrule
$+100$ & \$1{,}822 & --- \\
$+200$ & \$3{,}663 & \checkmark \\
$+300$ & \$5{,}522 & \checkmark \\
$+400$ & \$7{,}400 & \checkmark \\
$+500$ & \$9{,}297 (range exit) & \checkmark \\
\bottomrule
\end{tabular}
\end{table}

\noindent Zero violations occur across the five rows within the theorem's domain ($|\delta| \leq 500$ ticks for this 1,000-tick range). At $|\delta| = w/2$ the position fully exits range and the residual equals the full token1 balance minus what can be deposited at the new range's required ratio; additional Foundry runs at $|\delta| > w/2$ (not shown) plateau at this boundary value, consistent with saturation outside the theorem's domain.

\needspace{12\baselineskip}
\subsection{Theorem 5 (Directional Asymmetry)}

\begin{theorem}[Directional Asymmetry]
For a CL position in pool $(T_0, T_1)$ where $T_0$ is the volatile asset and $T_1$ is a stablecoin, symmetric sqrt-price displacements $\pm \delta$ from any in-range price $s$ produce asymmetric USD-valued outcomes. The up-move position retains strictly more USD value than the down-move position at all displacement magnitudes for which both $s + \delta$ and $s - \delta$ remain within the position's range.
\end{theorem}

\begin{proof}
The CL value function in token1 (stablecoin) units (Ryan, 2026a, eq.~3) is
\begin{equation}
V = L \cdot \phi(s, s_a, s_b)
\end{equation}
where $\phi(s, s_a, s_b) = 2s - s^2/s_b - s_a$. When token1 is a stablecoin, $V$ is already denominated in USD.

Let $s$ be any sqrt price within the position's range. For $\delta > 0$ such that $s_a \leq s - \delta$ and $s + \delta \leq s_b$ (both displaced prices remain in range), evaluate the difference:
\begin{equation}
V(s + \delta) - V(s - \delta) = L\left[\phi(s + \delta) - \phi(s - \delta)\right]
\end{equation}

Expanding:
\begin{align}
\phi(s + \delta) - \phi(s - \delta) &= 2(s + \delta) - \frac{(s + \delta)^2}{s_b} - s_a - 2(s - \delta) + \frac{(s - \delta)^2}{s_b} + s_a \notag \\
&= 4\delta - \frac{4s\delta}{s_b} = 4\delta\left(1 - \frac{s}{s_b}\right)
\end{align}

Since $s < s_b$ strictly for any position whose current price lies in the interior of its range, the factor $(1 - s/s_b) > 0$, and therefore $V(s + \delta) > V(s - \delta)$ for all $\delta > 0$ satisfying the range constraint.
\end{proof}

\noindent\textit{Remark (Residual--value bridge).} Theorem~1 of Ryan (2026a) gives the residual fraction $|\Delta R|/V$ as a function of range geometry and the current price, independent of $L$; at equal $|\delta|/w$, therefore, absolute residual magnitude scales with position value. Combined with Theorem~5, this implies that USD-denominated residual magnitudes inherit the directional asymmetry proved above, under the same pair-ordering and stablecoin assumptions. The theorem itself establishes only the $V$ inequality; the residual-magnitude statement follows as a scaling argument rather than an independent proof.

The asymmetry is numéraire-dependent. The proof measures value in token1 units, in which up-moves retain more value. Measured in token0 units, the reverse holds: down-moves retain more value. The mechanism itself is directionally blind; the apparent bias arises from the choice of unit of account. Since USD aligns with stablecoins (typically token1 in Uniswap V3 pair ordering), the USD-denominated accounting favours up-moves.

\medskip
\noindent\textit{Foundry verification.} Five symmetric displacement levels on a \$5,000 position.

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrr@{}}
\toprule
Displacement & Up value (USD) & Down value (USD) & Gap \\
\midrule
$\pm 100$ ticks & \$5,522 & \$3,663 & $+$\$1,859 \\
$\pm 200$ ticks & \$6,459 & \$2,740 & $+$\$3,718 \\
$\pm 300$ ticks & \$7,400 & \$1,822 & $+$\$5,577 \\
$\pm 400$ ticks & \$8,346 & \$908 & $+$\$7,437 \\
$\pm 450$ ticks & \$8,346 & \$0 & $+$\$8,346 \\
\bottomrule
\end{tabular}
\end{table}

\noindent Zero violations. The gap widens with displacement. At $\pm 450$ ticks both displaced prices approach the range boundaries; the down-move position has fully exited range, confirming the asymmetry extends to the boundary case.

\medskip
\noindent\textit{Empirical confirmation} ($N = 26{,}191$). Events classified by normalised displacement direction.

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
Direction & Events & Total Dust & Avg Dust & \% Positive \\
\midrule
Rising ($nd > 0.1$) & 17,879 & $+$\$1,129,420 & $+$\$63.17 & 35.6\% \\
Falling ($nd < -0.1$) & 8,312 & $-$\$103,308 & $-$\$12.43 & 36.2\% \\
\bottomrule
\end{tabular}
\end{table}

\noindent The proportion of events producing positive dust is near-identical (${\sim}36\%$ in both directions), confirming that the asymmetry is in magnitude rather than frequency. The USD-denominated dust flow is about $5\times$ larger during rising markets because token surpluses generated during rallies are valued at higher prices. (The dataset is not segmented by pool type; see \S\ref{sec:limitations}.)

\subsection{Theorem 6 (Exit Asymmetry)}

\begin{theorem}[Exit Asymmetry]
For a CL position in pool $(T_0, T_1)$ where $T_0$ is the volatile asset and $T_1$ is a stablecoin, a below-range exit retains less USD value than an above-range exit at symmetric sqrt-price displacement $d$ past the respective range boundary.
\end{theorem}

\begin{proof}
When the current sqrt price $s'$ exits the position's range $[s_a, s_b]$, the V3 amount equations reduce to boundary values:

At below-exit ($s' = s_a - d$, position is 100\% token0):
\begin{equation}
x_{\text{below}} = L \cdot (1/s_a - 1/s_b), \quad y_{\text{below}} = 0
\end{equation}

At above-exit ($s' = s_b + d$, position is 100\% token1):
\begin{equation}
x_{\text{above}} = 0, \quad y_{\text{above}} = L \cdot (s_b - s_a)
\end{equation}

The USD value of the above-exit position is $V_{\text{above}} = y_{\text{above}} = L(s_b - s_a)$, which is constant in $d$ since token1 is a stablecoin.

The USD value of the below-exit position is $V_{\text{below}} = x_{\text{below}} \cdot s'^2 = L(1/s_a - 1/s_b)(s_a - d)^2$, where $s'^2$ is the USD price of token0 at the current market sqrt price. This is strictly decreasing in $d$.

For any $d > 0$, the ratio $V_{\text{below}}/V_{\text{above}}$ decreases with $d$. The below-exit position loses value as the price moves further past the boundary, whilst the above-exit position does not.
\end{proof}

\noindent\textit{Remark (Redeployment).} To redeploy either terminal position into a new in-range position, the missing token must be obtained via swap. The below-exit position holds only token0, which has depreciated; the above-exit position holds only token1, which retains its full stablecoin value. Since $V_{\text{below}}$ decreases with $d$ whilst $V_{\text{above}}$ is constant, the below-exit position has strictly less capital available for redeployment at any $d > 0$.

\noindent\textit{Foundry verification.} Five symmetric exit distances past the range boundary.

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
Exit distance & Above value & Below value & Above swap frac & Below swap frac \\
\midrule
$\pm 50$ ticks & \$9,297 & \$0 & 0 bps & 9,999 bps \\
$\pm 100$ ticks & \$9,297 & \$0 & 0 bps & 9,999 bps \\
$\pm 200$ ticks & \$9,297 & \$0 & 0 bps & 9,999 bps \\
$\pm 300$ ticks & \$9,297 & \$0 & 0 bps & 9,999 bps \\
$\pm 500$ ticks & \$9,297 & \$0 & 0 bps & 9,999 bps \\
\bottomrule
\end{tabular}
\end{table}

\noindent The above-exit position retains its full stablecoin value (\$9{,}297) at all five distances. The below-exit position displays as \$0 in the test output because its USD value falls below the one-cent display threshold under integer arithmetic at depressed token0 prices; the token0 quantity is non-zero but negligible relative to the above-exit value. The swap-fraction columns report how much of the held token must be converted to obtain the missing token for redeployment: above-swap = 0~bps (the above-exit position already holds the stablecoin), below-swap = 9{,}999~bps (the below-exit position must convert almost everything). Across the five distances, the assertion $V_{\text{above}} > V_{\text{below}}$ holds at every row, and the swap-fraction asymmetry is confirmed at every row --- ten verifications in total.

\medskip
\noindent\textit{Empirical confirmation} ($N = 2{,}225$ exit events).

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrrr@{}}
\toprule
Exit type & Events & Avg Dust & Median & P5 (worst) & P95 (best) \\
\midrule
Above & 1,305 & $-$\$89 & $-$\$26 & $-$\$1,261 & $+$\$609 \\
Below & 920 & $-$\$141 & $-$\$29 & $-$\$1,479 & $+$\$961 \\
\bottomrule
\end{tabular}
\end{table}

\noindent Below exits produce 58\% larger average negative dust flow. The distribution tails are wider in both directions: P5 for below-exits is $-$\$1,479 versus $-$\$1,261 for above (17\% wider). Average tick displacement at exit is $+103$ ticks (above) versus $-88$ ticks (below). Theorem~6 predicts $V_{\text{below}} < V_{\text{above}}$ at the terminal state; the observed dust-flow asymmetry is consistent with this prediction via the residual--value bridge (Remark after Theorem~5), though the theorem does not prove a direct $|\Delta R|$ asymmetry for exit rebalances.

\section{Discussion}

Theorem~4 establishes that residual magnitude increases strictly monotonically with displacement up to the range boundary. Theorems~5 and~6 then show that position value is directionally asymmetric in USD terms for volatile/stablecoin pairs, even though the residual-generating mechanism is directionally blind. Because residual magnitudes scale with position value, USD-denominated residuals inherit these asymmetries.

The siphon moves tokens between positions through a shared dust pool based on geometric ratios. It does not take directional views. When these token flows are valued in USD, however, the accounting reflects the price exposure of the tokens being moved. In a portfolio where the volatile asset appears in multiple pools (a hub topology), token surpluses generated by rebalancing carry that asset's price exposure. The USD value of those flows therefore rises during rallies and falls during selloffs (Theorem~5), and below-range exits amplify this effect by retaining less USD value than above-range exits at symmetric displacement (Theorem~6). USD-denominated performance metrics will reflect the hub token's directional exposure.

\section{Foundry verification suite}

The directional theorems were verified against a mock pool implementing exact Uniswap V3 TickMath constants for sqrt-price and liquidity computations (\texttt{MockCLPoolV2}). The full Foundry suite is shared with the companion paper (Ryan, 2026a) and runs as 15 tests across four contracts:

\begin{verbatim}
cd foundry
forge test -vv --no-match-contract 'GeometricResidualProof$'
Suite result: ok. 10 passed; 0 failed; 0 skipped     (mock-pool tests)

RPC_BASE_ALCHEMY=https://mainnet.base.org forge test -vv
Suite result: ok. 5 passed; 0 failed; 0 skipped      (live fork tests)
\end{verbatim}

The mock-pool subset (10 tests) verifies the existence and scaling of the residual (Theorem~1), zero-swap extinction (Theorem~3), and the three directional theorems below. The live fork subset (5 tests) reproduces the Theorem~1 scenarios against unmodified Aerodrome Slipstream contracts on Base mainnet via \texttt{vm.createSelectFork}, exercising the same withdraw-mint sequence on real on-chain V3 geometry. The qualitative claims (residual existence, same-range control, linear scaling) hold deterministically; the exact residual values vary between runs as live pool state changes.

Tests 8--10 below verify the directional theorems introduced in this paper:

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Test & Theorem & Assertion & Result \\
\midrule
8  & Theorem 4 (monotonicity)          & 0 violations, 5 in-domain levels & PASSED \\
9  & Theorem 5 (directional asymmetry) & UP $>$ DOWN at all 5 levels  & PASSED \\
10 & Theorem 6 (exit asymmetry)        & 10/10 confirmations          & PASSED \\
\bottomrule
\end{tabular}
\end{table}

\noindent Tests 1--7 (Theorems 1 and 3 from Ryan, 2026a) and the five live fork tests are included for completeness and all pass.

\section{Limitations}\label{sec:limitations}

\begin{enumerate}
    \item \textbf{Empirical scope.} All empirical data come from one operator's positions on Aerodrome (Base). The theorem proofs are general, derived from the V3 amount equations, but the empirical ratios ($5\times$ directional asymmetry, 58\% exit asymmetry) are specific to this dataset and may differ under other protocols, pairs or market conditions.

    \item \textbf{Observation window.} 18 days of continuous operation. The dataset does not span a full market cycle.

    \item \textbf{Unsegmented pool composition.} The empirical confirmations for Theorems 5 and 6 ($N = 26{,}191$ directional events and $N = 2{,}225$ exit events) are drawn from the full Phase 3 dataset without segmentation by pool type. The reported ratios may therefore conflate volatile/stablecoin pools, to which the theorems strictly apply, with any other pool compositions present. Segmented analysis is left to future work.

    \item \textbf{Numéraire dependence.} Theorems 5 and 6 are proved in token1 units. Measured in token0 units, the inequalities reverse. The directional asymmetry is therefore an artefact of the chosen unit of account, not an intrinsic property of the mechanism. The USD interpretation holds when token1 is a stablecoin or when token1's USD price is approximately stable over the rebalance interval.
\end{enumerate}

\section{Conclusion}

In concentrated-liquidity rebalancing, the geometric residual increases strictly monotonically with displacement up to the range boundary (Theorem~4, Residual Monotonicity). For volatile/stablecoin pairs, position value is directionally asymmetric in USD terms (Theorem~5, Directional Asymmetry), and USD-denominated residuals inherit this asymmetry through the scaling of residual magnitude with position value. For the same pair ordering, below-range exits retain less USD value than above-range exits at symmetric displacement past the boundary (Theorem~6, Exit Asymmetry). All three results follow from the Uniswap V3 amount equations and are verified by Foundry tests using exact V3 \texttt{TickMath} constants for sqrt-price and liquidity computations.

The empirical dataset of 36,337 events across 58 positions and 18 days confirms the directional predictions at production scale: a $5\times$ magnitude difference in USD-denominated dust flows between rising and falling markets despite near-identical frequency of positive dust events, and $58\%$ larger average negative dust flow on below-range exits than above-range exits at comparable displacement.

Together with the existence (Theorem~1), equilibrium (Theorem~2) and extinction (Theorem~3) results established in Ryan (2026a), these three theorems extend the siphon framework to cover displacement magnitude, price direction and exit type. The properties are inherent to the V3 amount equations and should manifest in any system performing autonomous CL rebalancing with shared depositor balances.

\addcontentsline{toc}{section}{References}
\begin{thebibliography}{9}
\bibitem{adams2021}
Adams, H., Zinsmeister, N., Salem, M., Keefer, R. and Robinson, D. (2021) `Uniswap v3 Core', \textit{Uniswap Labs Technical Whitepaper}. Available at: \url{https://uniswap.org/whitepaper-v3.pdf}.

\bibitem{ryan2026a}
Ryan, K.R. (2026a) `The Geometric Siphon: Emergent Capital Reallocation in Concentrated Liquidity Portfolios'. Available at: \url{https://doi.org/10.2139/ssrn.6374838}.
\end{thebibliography}

\appendix
\newpage

\section{Foundry test reproduction}

Requirements: Foundry \texttt{forge} (installation instructions at \url{https://book.getfoundry.sh}) and, for the fork tests, any working Base RPC URL. The \texttt{forge-std} library is included as a git submodule; the \texttt{git submodule update} command below fetches it into \texttt{foundry/lib/forge-std}.

\begin{verbatim}
cd foundry
git submodule update --init --recursive

# Mock-pool tests only, no network access required (10 tests)
forge test -vv --no-match-contract 'GeometricResidualProof$'

# Full suite, including the 5 live fork tests (15 tests)
RPC_BASE_ALCHEMY=https://mainnet.base.org forge test -vv

# Directional theorem tests only (Tests 8-10 in NewTheoremsProof.t.sol)
forge test -vv --match-contract NewTheoremsProof
# Test 8: Monotonicity            0 violations across 5 in-domain levels
# Test 9: Directional asymmetry   5 symmetric moves, UP > DOWN at all levels
# Test 10: Exit asymmetry         10/10 below < above

# MockCLPoolV2.sol uses exact Uniswap V3 TickMath constants.
\end{verbatim}

\noindent The official public endpoint above is sufficient for all five fork tests; any Alchemy, Infura, QuickNode or other Base RPC URL is equally acceptable in \texttt{RPC\_BASE\_ALCHEMY}. Forge caches RPC responses locally, so repeat runs are fast; mock-pool tests complete in under a second. The captured \texttt{forge test -vv} output mapped to each theorem lives in \texttt{foundry/PROOF\_OUTPUT.md} and serves as the deterministic regression target for the mock-pool tests; fork-test residuals vary between runs as live pool state changes (the qualitative claims hold deterministically).

\section{Data and reproduction}

\begin{table}[H]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
Resource & Location \\
\midrule
Foundry verification suite & \texttt{foundry/} directory \\
Captured \texttt{forge test} output & \texttt{foundry/PROOF\_OUTPUT.md} \\
Phase 3 diffusion log & Available on request \\
\bottomrule
\end{tabular}
\end{table}

\noindent The repository is at \url{https://github.com/g4nc0r/the-geometric-siphon}; the Zenodo DOI \url{https://doi.org/10.5281/zenodo.19526374} resolves to an immutable archival snapshot of the repository at the time of deposit, whilst the GitHub URL tracks the latest commit. The Foundry suite reproduces all theorem verifications from a clean checkout (see Appendix~A). The Phase~3 diffusion-event log of 36{,}337 rebalance events across 58 positions used for the empirical confirmations in \S2 is available on request.

\end{document}
